Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-10 rnni_convexity.tex
problem with csort

The path $p$ returned by the algorithm $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.

>>>>

\todo{This is not enough, as sometimes one $\rnni$ move removes two inversions.}
The path $p$ returned by the algorithm $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.
